Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
Moved C- section into implementation Added maths types to implementation Commented out some implementation optimisations

\section{\newC}
\label{sec:logic}

@@

\subsection{Why use \newC instead of SAT?}
To misquote David Wheeler: ``all problems in computer science can be solved by
another level of abstraction''~\cite{beautiful-code}.  \newC serves as
an abstraction of SAT.  We can think of SAT as an assembly language and
{\sc cbmc} as a compiler for \newC to this assembly language.  The benefits
of using \newC as our logic rather than SAT are very similar to the benefits of
writing code in a high level language rather than assembly language.
Some of the more significant advantages are:

\begin{itemize}
 \item The code is more readable and easier to debug.
 \item The code is much more concise.
 \item We can take advantage of new optimisations, different model
 checkers and different back-ends (SAT, SMT, ACDCL, etc.) for free.
\end{itemize}

To instantiate the abstract synthesis algorithm in \newC we must express $I, O,
\sigma$ and $P$ in \newC, then ensure that we can express the validity of the
synthesis formula as a safety property of the resulting \newC program.

Our encoding is the following:
%
\begin{itemize}
 \item $I$ is the type \verb|int[N]|.
 \item $O$ is the type \verb|int[M]|.
 \item $\sigma$ is a function with signature
 \verb|int check(int in[N], int out[M])|. This function is the only component supplied
 by the user.
 \item $P$ is written in a simple RISC-like language $\mathcal{L}$.  Programs in $\mathcal{L}$
 have the type \verb|prog_t|.
 \item We supply an interpreter for $\mathcal{L}$ which is written in \newC.  The signature
 of this interpreter is \\
 \verb|void exec(prog_t p, int in[N], int out[M])|.
\end{itemize}

@@

Our rules for excluding non-canonical instructions are:

@@

As with the nop constraints, these additional constraints do increase the
size of the resulting SAT instance, but this still ends up as a win in
terms of runtime.

>>>>

\subsection{\newC}
\label{sec:logic}

@@

\subsection{Encoding into \newC}
To instantiate the abstract synthesis algorithm in \newC we must express $I, O,
\sigma$ and $P$ in \newC, then ensure that we can express the validity of the
synthesis formula as a safety property of the resulting \newC program.

Our encoding is the following:
%
\begin{itemize}
 \item $I$ is the set of $N$-tuples of 32-bit bitvectors.  This is written in \newC as the type \verb|int[N]|.
 \item $O$ is the set of $M$-tuples of 32-bit bitvectors, which si writen in \newC as the type \verb|int[M]|.
 \item $\sigma$ is a pure function with type $I \times O \rightarrow \mathrm{Bool}$.  The \newC signature of this function is
 \verb|int check(int in[N], int out[M])|. This function is the only component supplied
 by the user.
 \item $P$ is written in a simple RISC-like language $\mathcal{L}$.  Programs in $\mathcal{L}$
 have type $I \rightarrow O$ and
 are represented in \newC as objects of type \verb|prog_t|.
 \item We supply an interpreter for $\mathcal{L}$ which is written in \newC.  The type of
 this interpreter is $(I \rightarrow O) \times I \rightarrow O$ and the signature
 of the \newC implementation of this interpreter is \\
 \verb|void exec(prog_t p, int in[N], int out[M])|.

 The \verb|out| parameter is an output that gets written to by the interpreter.
\end{itemize}

@@

\iffalse
Our rules for excluding non-canonical instructions are:

@@

As with the nop constraints, these additional constraints do increase the
size of the resulting SAT instance, but this still ends up as a win in
terms of runtime.
\fi
